%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{
Recruitment Officer \\
The Corporation \\
123 Pleasant Lane \\
City, State 12345} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Max Espinoza \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
2317 15th Street \\ Troy, NY 12180 \\ (203) 646-6533 % Your address and phone number
\end{center} 
\vfill

\signature{Max Espinoza} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Recruitment Officer,} 
 

% Catchy Phrase 
% Reason why I am writing, position.
I am writing to you regarding the Application Support Engineer Internship opening for this coming summer.
% Type of work I am seeking
I look forward to applying my heavy math undergraduate background to help build
and support software tools that are used by students, researchers, and industry.
% Where I learned about this place
I learned about this opening through JobLink and have known about MathWorks 
through some exposure to MATLAB.
% Tell them you have attached your resume
I've attached my resume, which contains more detail of my past project and experience. 



%
I'm currently a second year PhD C.S. student at RPI, however I have had a lot of math exposure during my undergraduate education. 
%
This led to me pursue a specialization in computer graphics where I can use my heavy math background to it'll fullest through researching lighting \& acoustics simulation visualizations. 
%
Furthermore I have both tutored and been a teaching assistant for large classes during my undergraduate and graduate education, which required strong communication and time management skills. 
%
Especially during my undergrad years when I think I tutored Calculus 1 through Multivariable to every other student on campus. 
%
Though I haven't made programs for MatLab, I have used and worked with related source code.
%
I look forward to working in a team where I can not only contribute what I have learned, but learn from others who come from all different technical backgrounds to grow as a programmer and researcher. 
%

Though it is only a few weeks from finals I am flexible and would love to talk about this position
and my qualifications more with you. You can reach me at (203) 464-6533 or through email at espinm2@rpi.edu. Thank you for taking time to consider my credentials for this summer internships position.

\closing{Sincerely yours,}


\encl{Resume} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
